Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-08-21 draft.tex
reflection theorem
Update on Overleaf.

@@

>>>>

\begin{proof}
    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
    such that the $i$-th coordinate equals zero along $\hat F_i$.

    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.

    Let $f = \cartan u$ with $u \in \bfW^{p}\Lambda^{k}(T)$.
    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
    so that $\hat u \in \cartan \bfW^{p}\Lambda^{k}(\Delta^{n})$ and $\cartan \hat u = \hat f$.

    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.

    The operator norm bound of the potential operator shows 
    \begin{align*}
        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
        &\leq 
        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
        \\&
        \leq 
        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
        .
    \end{align*}
    We use the pullback estimates 
    \begin{gather*}
        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
        \leq 
        \| \Jacobian\varphi \|_{\infty}^{k}
        |\det\varphi^{-\frac{1}{p}}|
        \cdot 
        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
        ,
        \\
        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
        \leq 
        2^{n-l}
        \| \hat f \|_{L^{p}(\hat T)} 
        \leq 
        2^{n-l}
        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
        |\det\varphi^{\frac{1}{p}}|
        \cdot 
        \| f \|_{L^{p}(T)} 
        .
    \end{gather*}
\end{proof}

@@

% Please cite the original version:
% Alestalo, P., & Trotsenko, D. A. (2018). Radial extensions of bilipschitz maps between unit spheres. Siberian
% Electronic Mathematical Reports, 15, 839-843. https://doi.org/10.17377/semi.2018.15.071
% Theorem 3: radial extension of bi lipschitz between unit spheres, with same constant

We recall a specialization of this result.

\begin{lemma}\label{theorem:starreflection:facepatch}

% https://mathoverflow.net/questions/232302/lipschitz-constant-of-cental-projection-of-unit-ball-to-surface-of-convex-body
% https://eudml.org/doc/258483
% https://math.stackexchange.com/questions/1476085/uniformly-convex-approximation-of-convex-domain
% SMOOTH EXHAUSTION FUNCTIONS IN CONVEX DOMAINS
\begin{lemma}
    Let $K \subseteq \bbR^{n}$ be a compact set star-shaped with respect to the origin 
    that contains the ball $B_{r}(0)$ and that is contained in the ball $B_{R}(0)$. Then the function 
    \begin{align*}
        f : S \rightarrow \partial K, \quad x \mapsto \arg( \partial K \cap \bbR x )
    \end{align*}
    satisfies 
    \begin{align*}
        R^{2}/r % euclidean 
    \end{align*}
    If $K$ is convex, then 
    \begin{align*}
        g : S \rightarrow \bbR, \quad x \mapsto \| \bbR x \cap \partial K \|
    \end{align*}
    satisfies 
    \begin{align*}
        R \sqrt{ R^{2} / r^{2} - 1 } % angular distance 
        \\
        \frac R r \sqrt{ R^{2} - r^{2} } % angular distance 
    \end{align*}
\end{lemma}
\begin{proof}
    .
\end{proof}

### 2024-08-21 main.tex
Update on Overleaf.

@@

    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
    We write $w := \Bogov_{\ell} u$. 
    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\ell}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
    For any test form $v \in C^{\infty}\Alt^{n-\ell-1}(\Omega)$, 
    which is the restriction of some member of $C^{\infty}\Alt^{n-\ell-1}(\bbR^{n})$, 
    it holds that 
    \begin{align*}
        \int_{\Omega} v \wedge u_{i} 
        &=
        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
        +
        \int_{\Omega} v \wedge \cartan \Bogov_{\ell  } u_{i}
        \\&=
        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
        +
        (-1)^{k(n-k)+1}
        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
        .
    \end{align*}
    By the continuity of bounded linear functionals, we find 
    \begin{align*}
        \int_{\Omega} v \wedge u 
        &=
        (-1)^{k(n-k)+1}
        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
        .
    \end{align*}
    By definition, $w \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
    \todo{definition of weak derivative + definition of boundary condition }
    % 
    This completes the proof. 
\end{proof}

@@

\begin{lemma}    
    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
    For $0 \leq m < M$, write 
    $$
        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m},
        \qquad 
        I_{m} := X_{m} \cap T_{m+1}.
    $$ 
    Whenever $I_{m}$ is the union of $k$ different facets of $T$, 
    then the intersection of those facets is a simplex $S \in \calT$ of dimension $n-k$ that satisfies 
    $$
        \patch_{X_{m+1}}(S) = \patch_{\calT}(S).
    $$
\end{lemma}
\begin{proof}
    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
    that constitute the local patch around some simplex $S$ of dimension $n-k$.
    To show that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$, let us assume that $T \in \patch_{\calT}(S) \setminus \patch_{X_{m+1}}(S)$.
    By assumption, $S$ must be a boundary simplex of $X_{m+1}$. 
    \todo{Complete this here. The barycenter is contained in the interior of a boundary disk.}
\end{proof}

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
        M := |\patch_{\calT}(S)| \setminus T.
    There exists a bi-Lipschitz mapping
        \varphi : T \rightarrow M
    satisfying
        \Lip( \varphi,      T ) \leq \Cvier{n}{k} \kappa(\calT)^{2},
        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k} \kappa(\calT)^{2},
    where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$

@@

\todo{Summarize the next two lemmas into one and complete the estimate}
\begin{lemma}\label{lemma:PFexteriorwithboundaryconditions}
    Let $T$ be an $n$-simplex 
    and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
    Suppose that $u \in \bfW^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
    Then 
    \begin{align*}
        \| u \| 
        \leq 
    \end{align*}
\end{lemma}
\begin{proof}
    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
    such that the $i$-th coordinate equals zero along $\hat F_i$.

    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.

    Let $f = \cartan u$ with $u \in \bfW^{p}\Lambda^{k}(T)$.
    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
    so that $\hat u \in \cartan \bfW^{p}\Lambda^{k}(\Delta^{n})$ and $\cartan \hat u = \hat f$.

    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.

    The operator norm bound of the potential operator shows 
    \begin{align*}
        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
        &\leq 
        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
        \\&
        \leq 
        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
        .
    \end{align*}
    We use the pullback estimates 
    \begin{gather*}
        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
        \leq 
        \| \Jacobian\varphi \|_{\infty}^{k}
        |\det\varphi^{-\frac{1}{p}}|
        \cdot 
        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
        ,
        \\
        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
        \leq 
        2^{n-l}
        \| \hat f \|_{L^{p}(\hat T)} 
        \leq 
        2^{n-l}
        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
        |\det\varphi^{\frac{1}{p}}|
        \cdot 
        \| f \|_{L^{p}(T)} 
        .
    \end{gather*}
\end{proof}

\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
    Let $T$ be an $n$-simplex and with a face $F$. 
    If $u \in W^{p}\Alt^{k}(T)$ such that $\trace_{F} u = 0$, then 
    \begin{align*}
        \| u \|_{L^{p}(T)}
        &
        \leq 
        C_{{\rm PF},T,F,k,p} \| \cartan u \|_{L^{p}(T)}
        ,
    \end{align*}
    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
    \begin{align*}
        C_{{\rm PF},T,F,k,p}
        \leq 
        \diam(T)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
    Then $\cartan \hat u = \hat g$. 
    % 
    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
    We define $\tilde g = \cartan \tilde u$
    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
    \begin{gather*}
        \| \tilde u \|_{L^{p}(\hat U)} 
        \leq 
        C_{???} 
        \| \tilde g \|_{L^{p}(\hat U)}
        .
    \end{gather*}
    In addition to that, 
    \begin{gather*}
        \| u \|_{L^{p}(T_{m+1})}
        \leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \| \hat u \|_{L^{p}(\hat T)}
        \leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \| \tilde u \|_{L^{p}(\hat U)}
        ,
        \\
        \| \tilde g \|_{L^{p}(\hat U)}
        \leq 
        2^{\frac n p}
        \| \hat g \|_{L^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
        \| \cartan u \|_{L^{p}(T)}
        .
    \end{gather*}
    The second inequality follows.
\end{proof}

@@

    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
    First, there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
    \begin{gather*}
        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
    \end{gather*}
    %Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
    with $\cartan w_{m-1} = \cartan u$ over $\Omega_{m-1}$. 
    By assumption, $T_{m}$ and $\overline\Omega_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
    In accordance to Lemma~\ref{lemma:}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m} \subseteq \Omega_{m}$ be the complement of $T_{m}$ in that newly completed star.

    We define $w'_{m} := w_{m-1} \circ \Xi_{m} \in W^{p}\Alt^{k}(T_{m})$,
    where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
    as in Theorem~\ref{theorem:starreflection}. 
    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
    \begin{align*}
        \trace_F w_{m-1} = \trace_F w'_{m}
        . % TODO: notation, 
    \end{align*}
    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
    \begin{align*}
        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
        \quad 
        \trace_{\Gamma_{m}} w''_{m} = 0.
    \end{align*}
    Indeed, such $w''_{m}$ exists because 
    \begin{align*}
        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
        &= 
        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
        \\&= 
        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
        = 
        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
        = 
        0
        .
    \end{align*}
    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
    we find 
    \begin{gather*}
        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
        \\
        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
    \end{gather*}
    That means that $w_{m} \in W^{p}\Alt^{k}(\Omega_{m})$ with $\cartan w_{m} = \cartan u$ over $\Omega_{m}$.

    We want to estimate norms. 
    Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} gives 
    \begin{align*}
        \| w''_{m} \|_{L^{p}(T_{m})} 
        &
        \leq 
        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}
        \\&
        \leq 
        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        .
    \end{align*}
    We also employ Theorem~\ref{theorem:pullbackestimate} to find 
    \begin{align*}
        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
        \| \Jacobian \Xi   \|
        \cdot 
        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
        .
    \end{align*}
    By the properties of the reflection mapping in Theorem~\ref{theorem:starreflection},
    \begin{align*}
        ...
    \end{align*}
    Putting this all together, 
    \begin{align*}
        &
        \| w_{m} \|_{L^{p}(T_{m})}
        \\&
        \leq  
        \| w'_{m} \|_{L^{p}(T_{m})}
        + 
        \| w''_{m} \|_{L^{p}(T_{m})}
        \\&
        \leq  
        \rho(\calT)^{\frac 1 p} 
        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \left( 
            \| \cartan u \|_{L^{p}(T_{m})} 
            + 
            \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        \right) 
    \end{align*}
    and \todo{fix estimate}
    \begin{align*}
        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        &
        \leq  
        %C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        \\&
        \leq  
        \rho(\calT)^{\frac 1 p} \xi(\calT)
        %C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})} 
        \\&
        \leq  
        \rho(\calT)^{\frac 1 p} \xi(\calT)
        C%_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan u \|_{L^{p}(U_{m-1})} 
%         \\&
%         \leq  
%         \rho(\calT)^{\frac 1 p} 
%         \| w_{m-1} \|_{L^{p}(U_{m-1})} 
%         + 
%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
%         C_{{\rm PF},T_{m},\Gamma_{m},p} 
%         \| \cartan u \|_{L^{p}(T_{m})} 
        .
    \end{align*}
    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
\end{proof}

>>>>

A major structural feature of shellable simplicial complexes 
is that each time a simplex is added, the local star around a simplex gets completed.

\begin{lemma}\label{lemma:existenceofstar}
    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
    For $0 \leq m < M$, write 
    $$
        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m},
        \qquad 
        I_{m} := X_{m} \cap T_{m+1}.
    $$ 
    Whenever $I_{m}$ is the union of $k$ different facets of $T$, 
    then the intersection of those facets is a simplex $S \in \calT$ of dimension $n-k$ that satisfies 
    $$
        \patch_{X_{m+1}}(S) = \patch_{\calT}(S).
    $$
\end{lemma}
\begin{proof}
    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
    that constitute the local patch around some simplex $S$ of dimension $n-k$.
    To show that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$, let us assume that $T \in \patch_{\calT}(S) \setminus \patch_{X_{m+1}}(S)$.
    By assumption, $S$ must be a boundary simplex of $X_{m+1}$. 
    \todo{Complete this here. The barycenter is contained in the interior of a boundary disk.}
\end{proof}

@@

    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
    We write $w := \Bogov_{\ell} u$. 
    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\ell}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
    For any test form $v \in C^{\infty}\Alt^{n-\ell-1}(\Omega)$, 
    which is the restriction of some member of $C^{\infty}\Alt^{n-\ell-1}(\bbR^{n})$, 
    it holds that 
    \begin{align*}
        \int_{\Omega} v \wedge u_{i} 
        &=
        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
        +
        \int_{\Omega} v \wedge \cartan \Bogov_{\ell  } u_{i}
        \\&=
        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
        +
        (-1)^{k(n-k)+1}
        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
        .
    \end{align*}
    By the continuity of bounded linear functionals, we find 
    \begin{align*}
        \int_{\Omega} v \wedge u 
        &=
        (-1)^{k(n-k)+1}
        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
        .
    \end{align*}
    By definition, $w \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
    This completes the proof. 
\end{proof}

@@

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
    \begin{align*}
        M := |\patch_{\calT}(S)| \setminus T.
    \end{align*}
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \varphi : T \rightarrow M
    \end{align*}
    satisfying
    \begin{align*}
        \Lip( \varphi,      T ) \leq \Cvier{n}{k} \kappa(\calT)^{2},
        \quad 
        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k} \kappa(\calT)^{2},
    \end{align*}
    where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$

    \todo{Complete the estimate.}

@@

\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
    Let $T$ be an $n$-simplex 
    and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
    Suppose that $\bfu \in \bfW^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} \bfu = 0$ for $0 \leq i \leq l$.
    Then there exists $\bfw \in \bfW^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} \bfw = 0$ for $0 \leq i \leq l$
    and  
    \begin{align*}
        \cartan \bfu = \cartan \bfw,
        \quad 
        \| \bfw \| 
        \leq 
        C_{{\rm PF},T,F,k,p}
        \| \cartan \bfu \|
        ,
    \end{align*}
    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
    \begin{align*}
        C_{{\rm PF},T,F,k,p}
        \leq 
        ...
        \diam(T)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F_0$.
    We can also assume that the face of $\hat T$
    orthogonal to the $i$-th coordinate axis is mapped 
    onto the face $F_i$. 
    In what follows, we let $\tilde U$ be the domain obtained from reflecting $\hat T$ along the coordinate axes $l+1$ through $n$.

    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in \bfL^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
    Then $\cartan \hat u = \hat g$. 
    We let $\tilde u$ be the extension of $\hat u$ onto $\tilde U$ by reflection across the coordinate axes.
    We define $\tilde g = \cartan \tilde u$
    and see that $\tilde g$ is the extension of $\hat g$ onto $\tilde U$ by reflection across the coordinate axes. 
    By construction, $\tilde u \in \bfW^{p}_{0}\Lambda^{k}(\tilde U)$.

    The bounds for the potential operators imply 
    the existence of $\tilde w \in \bfW^{p}_{0}\Lambda^{k}(\tilde U)$
    with $\cartan \tilde w = \cartan \tilde u$ and 
    \begin{align*}
        \| \tilde w \|_{L^{p}(\tilde U)}
        &\leq 
        n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_2(0)) }{|\Omega|} 
        2
        \| \tilde g \|_{L^{p}(\tilde U)}
        \\&\leq 
        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{|\Omega|} 
        \| \tilde g \|_{L^{p}(\tilde U)}
        .
    \end{align*}
    We let $\bfw \in \bfW^{p}\Lambda^{k}(T)$ be defined by $\bfw := \varphi^{-\ast} \tilde w$.
    By construction, $\cartan \bfw = \cartan \bfu$,
    and $\bfw$ has vanishing trace along the faces $F_{0},\dots,F_{l}$.

    In addition to that, by Theorem~\ref{theorem:pullbackestimate}:
    \begin{gather*}
        \| \bfw \|_{L^{p}(T_{m+1})}
        \leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \| \tilde w \|_{L^{p}(\hat T)}
        \leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \| \tilde w \|_{L^{p}(\tilde U)}
        ,
        \\
        \| \tilde g \|_{L^{p}(\tilde U)}
        \leq 
        2^{\frac n p}
        \| \hat g \|_{L^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
        \| \cartan u \|_{L^{p}(T)}
        .
    \end{gather*}
    The second inequality follows.
\end{proof}

@@

    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
    First, there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
    \begin{gather*}
        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
    \end{gather*}
    %Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
    with $\cartan w_{m-1} = \cartan u$ over $\Omega_{m-1}$. 
    By assumption, $T_{m}$ and $\overline\Omega_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m} \subseteq \Omega_{m}$ be the complement of $T_{m}$ in that newly completed star.

    We define $w'_{m} :=  \Xi_{m}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m})$,
    where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
    as in Theorem~\ref{theorem:starreflection}. 
    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
    \begin{align*}
        \trace_F w_{m-1} = \trace_F w'_{m}
        . % TODO: notation, 
    \end{align*}
    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
    \begin{align*}
        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
        \quad 
        \trace_{\Gamma_{m}} w''_{m} = 0.
    \end{align*}
    Indeed, such $w''_{m}$ exists because 
    \begin{align*}
        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
        &= 
        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
        \\&= 
        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
        = 
        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
        = 
        0
        .
    \end{align*}
    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
    we find 
    \begin{gather*}
        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
        \\
        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
    \end{gather*}
    That means that $w_{m} \in W^{p}\Alt^{k}(\Omega_{m})$ with $\cartan w_{m} = \cartan u$ over $\Omega_{m}$.

    We want to estimate norms. 
    By construction,
    \begin{align*}
        \| w_{m} \|_{L^{p}(T_{m})}
        \leq  
        \| w'_{m} \|_{L^{p}(T_{m})}
        + 
        \| w''_{m} \|_{L^{p}(T_{m})}
        .
    \end{align*}
    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
    we can assume 
    \begin{align*}
        \| w''_{m} \|_{L^{p}(T_{m})} 
        &
        \leq 
        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}
        \\&
        \leq 
        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        .
    \end{align*}
    We also employ Theorem~\ref{theorem:pullbackestimate} to find 
    \begin{align*}
        \| w'_{m} \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
        \| \Jacobian \Xi \|^{k}
        \cdot 
        \| w_{m-1} \|_{L^{p}(U_{m-1})}
        ,
        \\
        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
        \| \Jacobian \Xi \|^{k+1}
        \cdot 
        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
        .
    \end{align*}
    We have assumed that $\cartan w_{m-1} = \cartan u_{|\Omega_{m-1}}$. 
    By the properties of the reflection mapping in Theorem~\ref{theorem:starreflection},
    \begin{align*}
        ...
    \end{align*}
    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
\end{proof}
